Applying the metallicity-dependent binary fraction to double white dwarf formation: \\ Implications for LISA

### 2022-10-03 src/tex/ms.tex
text edits

The ZAMS orbital period leads to different specific \textbf{He + He} 
evolutionary channels. For short-period systems with periods below 
$10~\rm{days}$, CE leads to a stellar merger due to insufficient orbital 
energy to eject the envelope. Stellar mergers continue to dominate the 
evolutionary pathways of systems with intermediate orbital periods ($1 < 
\log_{10}(P_{\rm{orb}}/\rm{day}) < 2.5$). However, an additional growing 
number of merging systems arises with one WD component and one stellar 
companion, and \textbf{surviving} systems which don't interact at all and 
thus do not form a He + He DWD. The distinction between the various 
scenarios in this intermediate orbital period range depends on the 
combination of their ZAMS masses and orbital periods. Finally, at wider 
initial periods $\log_{10}(\rm{P}) > 2.5$, the decrease in formation 
efficiency is dominated by systems which never interact and thus do not 
form a DWD before the present day.

@@

\subsubsection{\textbf{Parameter variations: CO + 
CO}}\label{formeff_CO_vars}
For CO + CO, across all variations, very close ZAMS binaries 
($P_{\rm{orb}}\sim\mathcal{O}(100$ days)) at high metallicities form a CO 
+ He or He + He DWD instead of a CO + CO because the binary interacts 
before core Helium burning of one or both components. There are again many 
more mergers in $\alpha25$, and fewer mergers for $\alpha5$. Due to the 
high CE efficiency of $\alpha5$, systems with shorter ZAMS orbital periods 
survive to become CO + CO DWDs rather than merging or becoming CO + He or 
He + He DWDs. There are fewer mergers overall for $q3$ than all the 
$\alpha$ variations because the first RLO occurrence leads to stable mass 
transfer from the primary to the secondary rather than multiple CE phases. 
For both the $\alpha5$ and $q3$ variations, the majority of CO + CO DWDs 
originate in wide enough orbits that they do not interact before DWD 
formation. This leads to an approximately constant formation efficiency 
across metallicity in both cases.

>>>>

The ZAMS orbital period leads to different specific \textbf{He + He} 
evolutionary channels. For short-period systems with periods below 
$10~\rm{days}$, \textbf{a CE phase} leads to a stellar merger due to 
insufficient orbital energy to eject the envelope. Stellar mergers 
continue to dominate the evolutionary pathways of systems with 
intermediate orbital periods ($1 < \log_{10}(P_{\rm{orb}}/\rm{day}) < 
2.5$). However, an additional growing number of merging systems arises 
with one WD component and one stellar companion, and \textbf{surviving} 
systems which don't interact at all and thus do not form a He + He DWD. 
The distinction between the various scenarios in this intermediate orbital 
period range depends on the combination of their ZAMS masses and orbital 
periods. Finally, at wider initial periods $\log_{10}(\rm{P}) > 2.5$, the 
decrease in formation efficiency is dominated by systems which never 
interact and thus do not form a DWD before the present day.

@@

\subsubsection{\textbf{Parameter variations: CO + 
CO}}\label{formeff_CO_vars}
For CO + CO, across all variations, very close ZAMS binaries 
($P_{\rm{orb}}\sim\mathcal{O}(100$ days)) at high metallicities form a CO 
+ He or He + He DWD instead of a CO + CO because the binary interacts 
before core Helium burning of one or both components. There are again many 
more mergers in $\alpha25$, and fewer mergers for $\alpha5$. Due to the 
high CE efficiency of $\alpha5$, systems with shorter ZAMS orbital periods 
survive to become CO + CO DWDs rather than merging or becoming CO + He or 
He + He DWDs. There are \textbf{fewer} mergers overall for $q3$ than all 
the $\alpha$ variations because the first RLO occurrence leads to stable 
mass transfer from the primary to the secondary rather than multiple CE 
phases. For both the $\alpha5$ and $q3$ variations, the majority of CO + 
CO DWDs originate in wide enough orbits that they do not interact before 
DWD formation. This leads to an approximately constant formation 
efficiency across metallicity in both cases.
